Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-08-15 batchdedup/analysis.tex
Updated performance model

In Stage 1a, the dirty segments are read from the virtual disk, the hash of
each block is computed, and dedup requests are sent to the machine hosting the
blocks' respective partitions. Due to the synchronization in each stage, Stage
1a needs to wait for the most heavily loaded machine to read all it's data - so
the read stage depends on $r_{max}$, while the write stage, which is balanced
by the hash partitioning, depends on $r$. We first read $r$ blocks from disk,
send $r$ dedup requests, and then save the received requests to temporary files
(one for each parition). The time for the first stage can be expressed as:
\[
    r_{max} c + \alpha_n\frac{u r_{max}}{m_n} / b_r + r u / b_w
\]

@@

The cost of Stage 1b is:
\[
    r u / b_r + (n e)b_r + r \beta + r e / b_w
\]

@@

The cost of Stage 2a is:
\[
    r(1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d2)}{m_n} + r_{max}(1-d_2)e / b_w
\]
and the cost of Stage 2b is:
\[
    r_{max}(1-d_2)(e+c) / b_r + r(1-d_2)c / b_b
\]

After the new blocks have been written to the block store, and references to
them have been obtained, those references must be returned to the parition
index holder so that those blocks may be deduped in the future (and also so
dup-with-new requests can be handled in this run). This Stage 3a, to read the
new index entries, return them to the parition index holder, and save the
received references, costs:
\[
    r (1-d_2)e / b_r + \alpha_n\frac{e r(1-d_2)}{m_n} + r(1-d_2)e / b_w
\]

Stage 3b consists of updating the partition index with the new block references
from Stage 3a, and also updating the dup-with-new results from Stage 1. First
we load the new references from Stage 2b into memory, and then dedup the
dup-with-new requests against the new block references and save the dup-with
new requests back to disk. We then add the new references to the corresponding
partition index to handle future dedup requests. Stage 3b costs:
\[
    r (1-d_2)e / b_r + r(1-d_2)e / b_w
\]

In the final stage (Stage 4), dup-with-new references are returned to the
requesters, so that the snapshot recipes may be updated with references to
those blocks. This process costs:
\[
    r d_3 e / b_r + \alpha_n\frac{e r d_3}{m_n} + r e / b_w
\]

Memory Requirments:\\
In every stage we need 1 disk read buffer, And then additionally we need the following:
\begin{description}
    \item[Stage 1a] network buffers, and $q$ disk write buffers
    \item[Stage 1b] $n/q$ partition index space, and $p$ disk write buffers (for dedup responses)
    \item[Stage 2a] network buffers, $v$ disk write buffers (for dedup responses)
    \item[Stage 2b] 1 disk write buffer (to write out new blocks)
    \item[Stage 3a] network buffers, $q$ disk write buffers (to write out new refs)
    \item[Stage 3b] 1 disk write buffer (to update patition index with new blocks)
    \item[Stage 4] network buffers, $v$ disk write buffers
\end{description}

>>>>

In Stage 1a, the dirty segments are read from the virtual disk, the hash of
each block is computed, and dedup requests are sent to the machine hosting the
blocks' respective partitions. Due to the synchronization in each stage, Stage
1a needs to wait for the most heavily loaded machine to read all it's data - so
the read stage depends on $r_{max}$, while the write stage, which is balanced
by the hash partitioning, depends on $r$. We first read $r$ blocks from disk,
send $r$ dedup requests, and then save the received requests to temporary files
(one for each parition). The time for the first stage can be expressed as:
\[
    r_{max} c / b_d + \alpha_n\frac{p u r_{max}}{m_n} + r u / b_w
\]

@@

The cost of Stage 1b is:
\[
    r u / b_r + n e / b_r + r \beta + r e / b_w
\]

@@

The cost of Stage 2a is:
\[
    r(1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d2) p}{m_n} + r_{max}(1-d_2)e / b_w
\]
and the cost of Stage 2b is:
\[
    r_{max}(1-d_2)(e+c) / b_r + r(1-d_2)c / b_b
\]

After the new blocks have been written to the block store, and references to
them have been obtained, those references must be returned to the parition
index holder so that those blocks may be deduped in the future (and also so
dup-with-new requests can be handled in this run). This Stage 3a, to read the
new index entries, return them to the parition index holder, and save the
received references, costs:
\[
    r_{max} (1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d_2) p}{m_n} + r(1-d_2)e / b_w
\]

Stage 3b consists of updating the partition index with the new block references
from Stage 3a, and also updating the dup-with-new results from Stage 1. First
we load the new references from Stage 2b into memory, and then dedup the
dup-with-new requests against the new block references. Once the dup-with-new
results have chunk references, we can add the dup-with-new results to the
duplicate result files. We then add the new references to the corresponding
partition index to handle future dedup requests. Stage 3b costs:
\[
    r ((1-d_2) + d_3)e/b_r + r (1-d_2)\beta + r((1-d_2) + d_3)e / b_w
\]

In the final stage (Stage 4), all duplicate references (including the
dup-with-new references from 3b) are returned to the requesters, so that the
snapshot recipes may be updated with references to those blocks. This process
costs:
\[
    r d_3 e / b_r + \alpha_n\frac{e r_{max} d_3 p}{m_n} + r e / b_w
\]

%Memory Requirments:\\
%In every stage we need 1 disk read buffer, And then additionally we need the following:
%\begin{description}
%    \item[Stage 1a] network buffers, and $q$ disk write buffers
%    \item[Stage 1b] $n/q$ partition index space, and $p$ disk write buffers (for dedup responses)
%    \item[Stage 2a] network buffers, $v$ disk write buffers (for dedup responses)
%    \item[Stage 2b] 1 disk write buffer (to write out new blocks)
%    \item[Stage 3a] network buffers, $q$ disk write buffers (to write out new refs)
%    \item[Stage 3b] 1 disk write buffer (to update patition index with new blocks)
%    \item[Stage 4] network buffers, $v$ disk write buffers
%\end{description}
